### 2022-07-26 paper/sections/numerical.tex
Small updates to paper draft

After creating the multicomponent ICs, the galaxies are evolved in isolation using \gadget for at least \drafting{$8\,\text{Gyr}$}, to ensure the systems are fully-relaxed and any potential effects arising from radial instabilities are mitigated. 
We then extract the evolved systems, and use these as the progenitors for all subsequent merger configurations.

@@

The progenitors are evolved through the \textit{parent phase} from $t(r_0)=0$ with \gadget until the SMBHs form a bound binary at $t_\text{stop}$, with a stellar softening of $\epsilon_\star=10\,\text{pc}$ and integration tolerances \drafting{check}.
We then initialise the \textit{child phase} by restarting from a snapshot sometime before $t_\text{stop}$.
We apply a small perturbation to each SMBH position and velocity vector to mimic the effect of Brownian motion due to discrete sampling of the DF, thus negating the need to run many simulations from $r_0=3\,R_\text{vir,1}$. 
The perturbations are drawn from a Gaussian distribution modelling the typical offset of the SMBH phase space coordinates from the phase space coordinates of the stellar centre of mass, determined using the shrinking sphere method. 
The Gaussian distributions are characterised by $\mathcal{N}_\text{pos}\sim(\mu=0\,\text{pc}, \sigma^2=100\,\text{pc})$, and $\mathcal{N}_\text{vel}\sim(\mu=0\,\text{km\,s}^{-1}, \sigma^2=100\,\text{km\,s}^{-1})$ for each progenitor \drafting{should we show a figure of this?}. 
From each \parent, we create ten uniquely-perturbed \child runs, allowing us to explore the distribution of parameters describing both the orbital and remnant properties of each \parent merger. 
Additionally, we lower the stellar softening to $\epsilon_\star=3.5\,\text{pc}$ and tighten the integration tolerances to \drafting{check} to optimise the run for \ketju.
We check for energy conservation between the \parent and \child runs, and confirm that the total energy is conserved at the sub-percent level. 
In total, we perform 360 ultra-high resolution unique \child simulations using \ketju, and use this sample for our analysis.

@@

>>>>

After creating the multicomponent ICs, the galaxies are evolved in isolation using \gadget for at least \drafting{$8\,\text{Gyr}$}, to ensure the systems are fully-relaxed and any potential effects arising from radial instabilities are mitigated. 
We then extract the evolved systems, and align each system with its reduced inertia tensor.
We use these as the progenitor galaxies for all subsequent merger configurations.

@@

The progenitors are evolved through the \textit{parent phase} from $t(r_0)=0$ with \gadget until the SMBHs form a bound binary at $t_\text{stop}$, with a stellar softening of $\epsilon_\star=10\,\text{pc}$ and \gadget integration tolerances \texttt{ErrTolIntAccuracy}=$0.02$ and \texttt{ErrTolForceAcc}=$0.005$.
We then initialise the \textit{child phase} by restarting from a snapshot sometime before $t_\text{stop}$.
We apply a small perturbation to each SMBH position and velocity vector to mimic the effect of Brownian motion due to discrete sampling of the DF, thus negating the need to run many simulations from $r_0=3\,R_\text{vir,1}$. 
The perturbations are drawn from a Gaussian distribution modelling the typical offset of the SMBH phase space coordinates from the phase space coordinates of the stellar centre of mass, determined using the shrinking sphere method. 
The Gaussian distributions are characterised by $\mathcal{N}_\text{pos}\sim(\mu=0\,\text{pc}, \sigma^2=100\,\text{pc}^2)$, and $\mathcal{N}_\text{vel}\sim(\mu=0\,\text{km\,s}^{-1}, \sigma^2=100\,\text{km}^2\text{\,s}^{-2})$ for each progenitor \drafting{should we show a figure of this?}. 
From each \parent, we create ten uniquely-perturbed \child runs, allowing us to explore the distribution of parameters describing both the orbital and remnant properties of each \parent merger. 
Additionally, we lower the stellar softening to $\epsilon_\star=3.5\,\text{pc}$ and tighten the integration tolerance \texttt{ErrTolIntAccuracy} to $0.002$ to optimise the run for \ketju.
We check for energy conservation between the \parent and \child runs, and confirm that the total energy is conserved at the sub-percent level. 
In total, we perform 360 ultra-high resolution unique \child simulations using \ketju, and use this sample for our analysis.

@@

\subsection{Bayesian Hierarchical Modelling}
\drafting{\begin{enumerate}
    \item HMC algorithm?
    \item Description of hierarchical model
    \item Prior distributions
    \item forward modelling
\end{enumerate}
}

### 2022-07-26 paper/sections/results.tex
Small updates to paper draft

\drafting{
Figures to do
\begin{itemize}
\item Good ones
\end{itemize}
Table of galaxy properties,
and maybe another one of BH merger remnant properties.
}

>>>>

\drafting{
Figures to do
\begin{itemize}
\item Example of forward-modelled semimajor axis and eccentricity
\item Example of forward-modelled density profile
\item Example of forward-modelled velocity dispersion profile
\end{itemize}
Table of galaxy properties,
and maybe another one of BH merger remnant properties.
}

\drafting{
    WHAT ARE THE MAIN OBSERVATIONS WE SEE and WHAT CONCLUSIONS CAN WE DRAW?
    \begin{enumerate}
        \item stability of hardening rate -> semimajor axis can be robustly predicted
        \item wide variance of eccentricity -> N-body models offer no quantitative prediction on likelihood of merger, can only comment on what merger looks like \textit{IF} it happens
        \item variance in observables: trends between observable properties and what observers can actually make use of (don't have this yet), e.g. signatures of SMBH scouring in velocity profile?
    \end{enumerate}
}
